### 2025-04-13 basic-statistics.qmd
20250413 - fixes

The kurtosis reflects the extent of extreme (outlying) values in a distribution relative to a normal distribution (or bell curve).
A mesokurtic distribution (with a kurtosis value near zero) reflects a normal amount of tailedness.
Positive kurtosis values reflect a leptokurtic distribution, where there are lighter tails and a sharper peak than a normal distribution.
Negative kurtosis values reflect a platykurtic distribution, where there are heavier tails and a flatter peak than a normal distribution.
Fantasy points tend to have a leptokurtic distribution.

>>>>

The kurtosis reflects the extent of extreme (outlying) values in a distribution relative to a normal distribution (or bell curve).
A mesokurtic distribution (with a kurtosis value near zero) reflects a normal amount of tailedness.
Positive kurtosis values reflect a leptokurtic distribution, where there are heavier tails and a sharper peak than a normal distribution, indicating more frequent extreme values.
Negative kurtosis values reflect a platykurtic distribution, where there are lighter tails and a flatter peak than a normal distribution, indicating fewer extreme values.
Fantasy points tend to have a leptokurtic distribution.
